\section{Introduction}

\subsection{Blockchain and Bitcoin}
Blockchain was introduced in 2008, by Satoshi Nakamoto, an anonymous programmer
(currently, it is probably a group of people) that designed with the aim to
create a virtual and decentralized currency, Bitcoin~\cite{satoshi}. Since
then, this technology has been developed and studied in different fields than
the financial one. Bitcoin and Blockchain rely on the digital signatures in
order to prevent the repudiation of a transaction, without a third party check.
To achive this, it was designed a peer-to-peer payment system, in which each
peer maintain a copy of the complete transaction history. Every transaction is
hashed, validated and stored in blocks connected in a list. These are created
by \textit{miners}, the members of the network, with a process called
\textit{mining}. The Blockchain history is agreed upon using a proof-of-work
system~\cite{pricing}~\cite{hashcash}, so each new block generated is rewarded.
Blockchain, as we said before, was designed in order to deal with
in particular Bitcoin and this systems becomes so popular because the it allows
to prevent double spending problem using transparent transactions, and it
preserve user personal privacy, giving them some sort of pseudo-anonymity.
In this system every user owns at least one wallet, that is associate with an
address. Addresses are 26-35 alphanumeric characters long and are indispensable
in order to be able to exchange Bitcoins. In fact to give Bitcoin to another
person you have to know her wallet address, that works as user account. It is
also possible to send money to non-existant addresses: when someone will create
a new wallet with that address it could redeem them. Each user could generate
more wallets and they does not require any kind of authentication. Often it is
raccomended to generate a new address to each transaction, in order to better
preserve the anonymity\cite{satoshi}. In order to use a certain address the
owner of the wallet must know the private key associate with it, in fact if it
will be lost there is no possibility to recover it. 


\subsection{Altcoins}
After the success of Bitcoin other digital currencies take place. All this
cryptocurrencies that are different from Bitcoin are colled \textit{altcoins}
(Alternative Coins)~\cite{bitcoinbeyond}. One of the most famous is 
\textbf{Ethereum}. A characteristics of this cryptocurrency is that in ... a
fork happened and we have two different version of this coins: \textbf{Ethereum
Classic} and \textbf{Ethereum}. Lots of aspects are similar to Bitcoin: even
this altcoin is based on blockchain, transactions are public, users are
pseudo-anonymous. In Ethereum wallets are associated with 40 alphanumeric
characters addresses that could has as prefix \texttt{0x}. Three other altcoins
that has public transactions (and that we deal with in this work) are 
\textbf{Bitcoin Cash}, \textbf{Litecoin} and \textbf{Dogecoin}. The first one
is a hard fork of Bitcoin performed in 2017. Addresses format are the same of
the original coin. The second one, instead, is a criptocurrency born in 2011
with the aim to improve Bitcoin and thought to be ``lighter'' to create blocks.
Litecoin wallets starts with \texttt{L} or \texttt{M} followed by an
alphanumeric string whose length is between 24 and 36 characters. The latter
is an altcoin born as a joke in 2013 but that rapidly increased its value,
exeeding 1 billion dollars in January 2018. Dogecoin addresses starts with
\texttt{D} followed by 33 alphanumeric characters.

\subsection{Pseudo-anonymity in Bitcoin system}
We can define a subject as anonymous if subject is not identifiable within a
set of subjects, denoted as the anonymity set~\cite{terminology}. Bitcoin system
does not provide it because I) The real-name authentication mechanism
helps Bitcoin service providers to find the addresses that ever deposited and
withdrew; II) a Bitcoin wallet advertised on Internet can be related to its
owner; III) the chain of transactions is transparent; IV) exchanging inputs
from an address to another one could expose the sender; V) the change address
of transactions could be classified by attackers to the sender~\cite{deanon}.
So in that context we can speak about pseudo-anonymity: until a user does not
associate personal information with a certain wallet, she could be considered
anonymous.