\section{Related work} \label{relworks}
As the popularity of Bitcoins and altcoins grow, the number of work on
de-anonymization of their transactions increases.
There are mainly two kinds of approaches.

The first method exploits the structure of the underlying p2p network on which
the blockchain relies to attack anonymity of transactions.
In~\cite{bib:anonBitcoin} the authors propose a system in which they bind IP
addresses to transactions to define the ownership of transactions. Another
valuable study is~\cite{bib:deanonP2P}. In the latter the authors propose an
attack to Bitcoin infrastructure that they claim to work even in challenging
scenarios (e.g. bypassing firewalls and NATs) with a few number of computers.
We do not follow this idea because we do not want to bind IP addresses to
transaction, but rather physical person to transaction. Another problem is that
this kind of approach could be computationally heavy. The other technique,
instead, has no requirements on the computational power.

An orthogonal approach, that is the one that we followed, is to search for
public information on the Web in order to find out the wallets advertised
by the owner and afterwards infer other related wallets. This approach is used
in~\cite{bib:anonAnalysis}: the authors retrieved public available addresses
from Bitcoin dedicated forums in order to discover related wallets. This
approach is explained with a graph view of the transaction occurred in the
blockchain: addresses are the vertexes and transactions are the edges. In this
graph, called \textit{user graph} addresses inputs of the same transaction are
clustered in a single node because owned by the same person. This privacy
problem was for the first time issued by Satoshi Nakamoto and comes out
because people do not generate new wallets for each transaction as he
suggested~\cite{bib:satoshi}. Another work based on that idea
is~\cite{bib:fistful}.
These works are pretty old (they were published in 2011) and they focus only on
Bitcoins and in retrieving addresses from Bitcoin forums. A possible issue is
the multi-signature native support of Bitcoins. This requires that a
transaction, to be valid, is signed with more than a single public
key~\cite{bib:multisignature}: in this scenario all this addresses will be
grouped in the same cluster. A more fine grained study of this cluster will
probably find out the differences, if integrated with different techniques. We
must consider that the use of multi-signature wallets typically involve closely
related people~\cite{bib:multisignaturebitcoinwiki}, so for certain application
can be useful to group this people together.

Other related studies focus on transaction profiling.
In~\cite{bib:fullDiscl} is
proposed a profiling transaction model in the Bitcoin environment. The
simplest example is the following: if we have 2 addresses and the first one
sends periodically the same amount of Bitcoins in US Dollars, then probably
the person who owns the second wallet works for the first one.

In this research we do not consider de-anonymization in scenarios in which are
used \textit{mixing} services. These kind of services are used to augment
transactions' anonymity: basically they put some noise in the transaction
history to make it harder to identify senders and receivers.
% basically, a user sends money to these services that
% are mixed and gave back to the initial user generating new addresses. 
These anonymizing techniques are largely used in illegal purchase or money
laundering~\cite{bib:laundering}.
